Comparing vector-based and ACT-R memory models using large-scale datasets:\protect\\User-customized hashtag and tag prediction on Twitter and StackOverflow

### 2014-12-03 writeups/dissertation/dissertation.tex
foo

Co-occurrence-based modeling has been shown as a potentially useful approach when predicting Twitter hashtag use \parencite{Efron2010} and StackOverflow tag use \parencites{Stanley2013}
Several memory retrieval models are based on this broad methodology, where a count is maintained of the times each contextual element (such as a word in a post) co-occur with a tag.
At least two of the current memory retrieval models are based on a co-occurrence methodology:
ACT-R's declarative memory (DM) retrieval theory and random permutation vector-based memory systems.

>>>>

Co-occurrence-based modeling has been shown as a potentially useful approach when predicting Twitter hashtag use \parencite{Efron2010} and StackOverflow tag use \parencites{Stanley2013}.
Several memory retrieval models are based on this broad methodology, where a count is maintained of the times each contextual element (such as a word in a post) co-occur with a tag.
At least two of the current memory retrieval models are based on a co-occurrence methodology:
ACT-R's declarative memory (DM) retrieval theory and random permutation vector-based memory systems.
